---
title: "CorN"
author: "Database of Corn N trials in Kansas"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: css/styles.css
runtime: shiny
---

```{r setup, include=FALSE}
# Libraries ----

## 1. App ----
library(shiny)
library(flexdashboard)
library(shinydashboard)
library(shinythemes)
library(shinyWidgets)

## 2. Map -----
library(leaflet)
library(sf)
library(tigris)

## 3. Data manipulation ----
library(dplyr)
library(tidyverse)

## 4. Graphs ----
library(ggplot2)
library(quantreg)
library(plotly)
library(nlstools)

# Data import ----
countiesNames <- read.csv("data/trials.csv", sep=",", dec=".")
# countiesBorders <- st_read("Kansas_Counties/Tiger_2020_Counties.shp")
datafcurves <- read.csv("data/curves.csv", sep=",", dec=".")
countiesBorders <- tigris::counties(state = "KS", class = "sf")


# Function import ----
source(file = "quadratic_plateau.R")
library(nlraa)

datafcurves <- datafcurves %>%
  mutate(yield_bu = Yield * 15.93,
         nrate_lbs = Nrate *0.89)


```


Visualization
=======================================================

Column {data-width=300}
-------------------------------------------------------

### Inputs

```{r}

# Select for counties -----
counties <- subset(countiesNames, select = c(1))

shinyWidgets::pickerInput(inputId = "countiesSelection",
                          label = h6("Select counties or whole state: "),
                          choices = counties,
                          multiple = TRUE,
                          options = list(`actions-box` = TRUE),
                          selected = c("Riley", "Greeley", "Shawnee", "Franklin", "Republic", "Jefferson", "Marshall", "Osage", "Reno", "Thomas", "Barton", "Labette")
        )

hr()

# N price -----
shiny::sliderInput(inputId = "NCost",
                   label = h6("Select the actual Nitrogen source cost (US$/lbs N)"),
                   value = 1, 
                   min = 0.5,
                   max = 1.5,
                   step = 0.05)

hr()

# Corn price -----
shiny::sliderInput(inputId = "cornPrice",
                   label = h6("Select the actual selling corn price (US$/bu)"),
                   value = 6.8, 
                   min = 2,
                   max = 8,
                   step = 0.1)

hr()

# QR Code image ----

h6("How can we improve it? Answer the survey!")
tags$img(src = "www/Survey.png", height = "150px", width = "150px")



```


Column {data-width=750}
-------------------------------------------------------

### Probable Response Curve

```{r}

# Filtering data ----
datafplot <- reactive({

  datafcurves %>%
    dplyr::filter(County %in% input$countiesSelection) %>%
    dplyr::select(c(Nrate, Yield, nrate_lbs, yield_bu))

})

# Transforming in quadratic plateu ----
QP_Fit <- reactive({

   quadratic_plateau(data = datafplot(),
                     yield = yield_bu,
                     Nav = nrate_lbs,
                     plot = FALSE,
                     tidy = TRUE)

})



# Creating curve ----
output$responseCurve <-  renderPlotly({

   plot <- ggplot(data = datafplot(),
                    aes(y = datafplot()$yield_bu,
                        x = datafplot()$nrate_lbs))+
     geom_point(size = 1, alpha = 0.5, color = "orange") +
     geom_line(stat="smooth",
            method = "nls",
            formula = y ~ SSquadp3xs(x, a, b, jp),
            se = FALSE,
            color = "steelblue") +
     geom_quantile(quantiles=c(0.10, 0.90), formula= y ~ poly(x,2),
                   colour="#A6808C", linetype = "dashed", size = 0.5)+
     geom_vline(xintercept = Optimums()$AOD, size = 1,
                linetype = "dashed", color = "steelblue") +
     geom_vline(xintercept = Optimums()$EOD, size = 1,
                linetype = "dotted", color = "#a6808c") +
     ggplot2::annotate("pointrange",
                       shape = 25, size = 4,
                       x = Optimums()$AOD, y = 0,
                       xmin = Optimums()$AOD, xmax = Optimums()$AOD,
                       color = "grey15", fill = "steelblue") +
     ggplot2::annotate("pointrange",
                       shape = 25, size = 4,
                       x = Optimums()$EOD, y = 0,
                       xmin = Optimums()$EOD, xmax = Optimums()$EOD,
                       color = "grey15", fill = "#a6808c")+
   ggplot2::annotate("text",
                     label = paste(paste("Equation: ",
                                         QP_Fit()$equation),
                                   paste("R2 = ", QP_Fit()$R2), sep="\n"),
                            x = 50, y = 10,
                            hjust = 1.5,vjust = 1.5, col = "grey25")+
     scale_y_continuous(breaks = seq(0,300, 25))+
    scale_x_continuous(breaks = seq(0,300, 25))+
   theme_bw()+
     labs(x = "N fertilizer applied (lbs N/ac)",
          y = "Corn Yield (bu/ac)")+
     theme(panel.grid = element_blank(),
           axis.text.x = element_text(size=rel(0.8), color = "#330a57"),
           axis.text.y = element_text(size=rel(0.8), color = "#330a57"),
           strip.text = element_text(size=rel(0.5), color = "#330a57"))

  ggplotly(plot)

 })


# Displaying the plot -----
plotlyOutput(outputId = "responseCurve")

```

Column {data-width=300}
-------------------------------------------------------

### Counties Selected

```{r}

# Filtering from user input -----
selectedCounties <- reactive({

  countiesSelected <- countiesBorders %>%
    dplyr::filter(NAME %in% input$countiesSelection)

  countiesSelected

})

# Generating Map ----
output$countiesMap <- renderLeaflet({

    leaflet(width = 200, height = 300) %>%
          setView(lng = -98, lat = 38.5, zoom = 05) %>%
          addTiles() %>%
          addPolygons( data = countiesBorders,
                       weight = 1,
                       smoothFactor = 0.2,
                       fillOpacity = 0.2,
                       color = "black",
                        highlight = highlightOptions(
                             weight = 5,
                             color = "#666666",
                             fillOpacity = 0.25,
                             bringToFront = TRUE
                           )
            ) %>%
          addPolygons( data = selectedCounties(),
                       weight = 1,
                       smoothFactor = 1,
                       fillOpacity = 1,
                       color = "#330a57",
                        highlight = highlightOptions(
                             weight = 5,
                             color = "#666666",
                             fillOpacity = 0.5,
                             bringToFront = TRUE
                           )
            )


})

# Showing the map ----
leafletOutput("countiesMap", height = 600)

```


### Price Ratio

```{r}

# Getting price ratios ------
priceRatio <- reactive({
  
  out <- round(as.numeric(input$NCost/ input$cornPrice), 2)
  
  out

})

# Plotting price ratio gauge ------
flexdashboard::renderGauge({
  
  flexdashboard::gauge(priceRatio(),
                       min = 0,
                       max = 0.6,
                       symbol = '',
                       label = "Price Ratio",
                        gaugeSectors( success = c(0,0.1),
                                      warning = c(0.101,0.15),
                                      danger = c(0.151, 0.3),
                                      colors = c("#2a9d8f", "#fcbf49", "#ce4257"))
                        )
  
})


# Discovering Optimums ----
Optimums <- reactive({
  
   QP_Fit() %>%
    mutate(AOD = CSTV,
           EOD = (priceRatio() - slope) / (2*(-slope / (2*AOD))),
           EOD = ifelse(EOD >= 0, 
                         EOD, 0)
           )
  
})

```

### Agronomic Optimum Rate

```{r}

# Agronomical Optimum Dosis ----
flexdashboard::renderValueBox({
  
  flexdashboard::valueBox(paste(round(Optimums()$AOD,0), "lbs N/ac"), 
            h6("Agronomic Optimum Rate"), 
            icon = "fa-seedling", 
            color = "#166e95")
  }) 

```

### Economical Optimum Rate

```{r}

# Economical Optimum Dosis -----
flexdashboard::renderValueBox({
  
  flexdashboard::valueBox(paste(round(Optimums()$EOD,0), "lbs N/ac"), 
            h6("Economical Optimum Rate"), 
            icon = "fa-coins", 
            color = "#ee826c")
  })

```

### Trials in selected counties

```{r}


# Getting number of trials  -----
ntrials <- reactive({
  
  numberOfTrials <- countiesNames %>%
    dplyr::filter(County %in% input$countiesSelection) %>%
    dplyr::summarise(Number = sum(Trials))
  
  numberOfTrials
  
})

# Displaying number of trials -----
flexdashboard::renderValueBox({
  
  flexdashboard::valueBox(ntrials(),
                          h6("Trials in selected counties"),
                          icon = "fa-flag",
                          color = "#d9575b")
  })


```


About
=======================================================

Column {data-width=100}
-------------------------------------------------------
```{r}

tags$img(src = "www/images.png", height = "150px", width = "250px")
br()
tags$img(src = "www/KCARE_logo_purple.png", height = "250px", width = "250px")
br()
tags$img(src = "www/image.png", height = "150px", width = "250px")

```



Column
-------------------------------------------------------
### Description
<p style="text-align: justify; padding: 20px"> This tool was developed by <a href="https://github.com/GustavoSantiago113">Gustavo N. Santiago</a> and <a href="https://github.com/adriancorrendo">Adrian Correndo</a>, members of <a href = "https://ciampittilab.wixsite.com/ciampitti-lab">Ciampitti Lab</a> at <a href="https://www.k-state.edu/">Kansas State University (KSU).</a> </p>
<p style="text-align: justify; padding: 20px">The data used on this tool was gathered from several works developed by KSU personnel among different years and counties across Kansas. Using this tool, a farmer can know, based on their region, the economical and agronomic optimum rate for his/her corn. The agronomic optimum rate is obtained from the trials and the response of a quadratic plateau formula. The economical optimum rate is obtained from the agronomic optimum rate, combined with the price ratio inserted by the user.</p>



